---
title: "R Notebook"
output: html_notebook
---



### d) Recreate figure 3a (main) but change the y-axis to be the raw mention count, not rate of mentions

Reading in data
```{r}
rm <- read.csv('C:/Users/fks5029/Documents/GitHub/SoDA-501/EX02/googlebooks-filtered-1850-2008.csv',header=TRUE,sep=",")
```

Plotting raw data
```{r}
onegram <- c(1883,1910,1950)
library(ggplot2)

df <- rm[rm$term %in% onegram, ]
ggplot(df, aes(x=year, y=term_count))+geom_line()+xlab('Year')+ylab('Frequency')+ggtitle('Replication of 3A with Raw Mention Count')
```





Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
